Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-08 draft.tex
add legends to explanation figures / add referenced to the figures in the text
some phrasing changes

			explanation is in the following section. Figure \ref{fig:model_plot} depicts the

@@

			of the dataset, differing depending on the exact experiment (more details are provided
			in the next section). Evaluation was then performed on the remaining samples in the
			dataset. Training batches consisted of 100 samples each with every window position for
			each sample and an upper limit of 1,000,000 lines per batch. For each batch, either
			one or two epochs were performed. Because a single sample can have multiple input
			lines, evaluation cannot be performed on a per-line basis, but must instead be
			summarized. Two methods are possible: median and mean, with the difference in results
			being negligible in our experiments. The default threshold is 0.5, meaning that a
			result under 0.5 is a negative result and over 0.5 is a positive result. This
			threshold can however be adjusted, useful for computing certain metrics.

@@

			\label{figure:exp_cterm}

@@

			\label{figure:exp_mpf}

@@

			\label{figure:exp_mpf_cterm}

@@

		\ref{table:exp-results-more-pitch-flucs} and \ref{table:exp-results-mpf-cterm}. 

>>>>

			clarification is in the following section. Figure \ref{fig:model_plot} depicts the

@@

			of the dataset, with the exact size of the training set differing depending on the
			exact experiment (more details are provided in the next section). Evaluation was then
			performed on the remaining samples in the dataset. Training batches consisted of 100
			samples each with every window position for each sample and an upper limit of
			1,000,000 lines per batch. For each batch, either one or two epochs were performed.
			Because a single sample can have multiple input lines, evaluation cannot be performed
			on a per-line basis, but must instead be summarized. Two methods are possible: median
			and mean, with the difference in results being negligible in our experiments. The
			default threshold is 0.5, meaning that a result under 0.5 is a negative result and
			over 0.5 is a positive result. This threshold can however be adjusted, useful for
			computing certain metrics.

@@

			\label{fig:exp_cterm}

@@

			\label{fig:exp_mpf}

@@

			\label{fig:exp_mpf_cterm}

@@

		\ref{table:exp-results-more-pitch-flucs} and \ref{table:exp-results-mpf-cterm}. The same
		statistics are also represented graphically in the figures \ref{fig:exp_cterm},
		\ref{fig:exp_mpf} and \ref{fig:exp_mpf_cterm} respectively.
